---
title: "Shiny App"
author: "Kamlesh Mishra"
date: "September 6, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

## Slides for Shiny App Project

This shiny apps developed using shiny platform. The objective of this apps is to have below requirements:-

  - Some form of input (widget: textbox, radio button, checkbox, ...)
  - Some operation on the ui input in sever.R
  - Some reactive output displayed as a result of server calculations
  - You must also include enough documentation so that a novice user could use your application. 
  - The documentation should be at the Shiny website itself. Do not post to an external link.
  
    
## Shiny Apps Features & Functions

This is a Shiny App Project that was developed to show the various widgets that can be used to the App.

  - This App have two sections, a sidebar which is on the left of the App and on the right is     main screen that contains the tabs.
  - The sidebar panel have fours(4) control items.
  - Title textbox allow user to customize the main page title description.
  - The second (2) control item allows the user to select dataset
  - Third item is to controls on how many observatrions will be showed under the Table tab.
  - The forth control allow the use to select the color of the histogram.


## Shiny Apps Project

The shiny apps can be viewed at this page
https://kamleshm18.shinyapps.io/Shiny_App_Project/

### Shiny Github Repo Project & Code Reproducibility

The code for the shiny apps can be downloaded from the github repo at
https://github.com/kamleshmishra18/Developing_Data_Product

This repo contains all the code and data making up this solution. The files and folders are the following:

  - README.md
  - app.R, ui.R and server.R - The shiny app code/presentation
  - The R Markdown used to create the RStudio Presenter presentation.



## Samples of information generated

Below are the summary and header generated for the dataset InsectSprays

```{r}
library(MASS)
library(datasets)
summary(Animals)
```